Balsa: A Compact Line Notation Based on SMILES

### 2022-07-31 manuscript.tex
Notes that selection is optional and equivalent to setting bond orders. Closes #37

>>>>

Selection is nothing more than an alternative to explicit bond order encoding. No other properties whatsoever are conferred to selected atoms. The members of a DS may be assigned the labels \enquote{aromatic,} \enquote{antiaromatic,} \enquote{non-aromatic,} or any number of other designations by downstream applications. Two encodings differing only in the presence of a DS should be considered equivalent. Balsa itself provides no guidance at all about whether or not selectable atoms should be selected, although individuals and organizations may do so.
